SMT-Boosted Security Types for Low-Level MPC

### 2025-11-24 toplas26/smt.tex
checkpoint

\begin{proof}
  \cnote{de-obfuscate.}
  Assume $\htrip{\eqs_1}{\prog}{\eqs_2}$ is derivable without \TirName{Hyp}.
  Then $\eqs_1 \wedge \toeq{\prog} \models \eqs_2$, since all the other rules
  are well-known to be validity preserving. 
  Now since $\eqs_1 \wedge \toeq{\prog} \models \eqs_2$ by assumption, we have
  $
  \eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog} \models \eqs_2 
  $,
  and clearly:
  $$
  \eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog} \models \eqs_2 \wedge (\eqs_2 \impl \eqs)
  $$
  and since $\eqs_2 \wedge (\eqs_2 \impl \eqs)$ iff
  $\eqs_2 \wedge \eqs$, we have
  $\eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog} \models \eqs_2 \wedge \eqs$.
\end{proof}

>>>>

\begin{proof}
  By induction on the derivation and cases analysis on the last derivation
  step. We only need to consider $\TirName{Hyp}$ since other cases are standard.
  In this case the consequent is of the form
  $\htrip{\eqs_1 \wedge (\eqs_2 \impl \eqs)}{\prog}{\eqs_2 \wedge \eqs}$
  where $\htrip{\eqs_1}{\prog}{\eqs_2}$ is derivable by inversion
  of \TirName{Hyp} and hence valid by the induction hypothesis.
  Thus $\eqs_1 \wedge \toeq{\prog} \models \eqs_2$,
  %, and
  % therefore in particular $\eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog}$
  % iff $\eqs_1 \wedge \eqs \wedge \toeq{\prog}$. Now 
  and we can strengthen the condition on the rhs of $\models$:
  $$
  \eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog} \models \eqs_2 
  $$
  so by standard reasoning we have:
  $$
  \eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog} \models \eqs_2 \wedge (\eqs_2 \impl \eqs)
  $$
  and since $\eqs_2 \wedge (\eqs_2 \impl \eqs)$ iff
  $\eqs_2 \wedge \eqs$, we have
  $\eqs_1 \wedge (\eqs_2 \impl \eqs) \wedge \toeq{\prog} \models \eqs_2 \wedge \eqs$.
\end{proof}
